Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2019-08-14 peakcharacterization_manuscript.Rmd
correct variable
figure for sliding window non-zero points

@@

```{r peak_ordering}
drake::loadd(plot_peak_ordering)
plot_peak_ordering
```

@@

```{r slidingwindow_count_distribution}
# Figure showing distribution of nonzero counts
```

>>>>

*caption*: **A**: Intensity vs M/Z for a single peak from a single scan. Red lines denote the differences between each point, and red dots the average between the pair of points. The difference over the point is used to derive the frequency values in **B**. **B** plots the intensity vs the converted frequency points derived from **A**. The red lines denote pairwise differences, which are shown in **C** for this single peak. The differences for all peaks across all scans vs M/Z are shown in **D**, with those differences that lie within 0.49 - 0.51 shown in red. **E** shows the plot of derived frequency *vs* M/Z, with fitted values from the linear model in red.

@@

```{r peak_ordering}
drake::loadd(peak_ordering)
peak_ordering
```

@@

```{r slidingwindow_count_distribution}
drake::loadd(sliding_regions)
sliding_regions
```
